### 2019-01-06 draft.tex
addressed alis comments

Matings between sufficiently diverged populations or species produce low fitness hybrids, or fail altogether, due to the action of intrinsic incompatibilities \citep{dobzhansky1937, muller1942} or ecological barriers \citep{schluter1998}. %YANIV DOUBLE CHECK THIS REFERENCE IS ABOUT ECOLOGICAL BARRIERS
Misallocated reproductive effort spent on producing low fitness hybrids can be prevented through natural selection favoring prezygotic barriers, a process known as reinforcement \citep{dobzhansky1937, servedio2003}.
Reinforcement is generally conceptualized as the evolution of an assortative mating locus \citep{felsenstein1981} or female preference locus \citep{servedio1997}.   
Both reinforcement mechanisms assume males and females have a shared interest in preventing the production of low-fitness hybrid offspring. 
However, reproductive interactions are generally more fractious than this, as the costs of reproductive effort can differ by sex and reproductive stage (ranging from gamete formation to mating itself) \citep{arnqvistandrowebook}.  
Because male and female interests are not always aligned, interspecific sexual conflict over the hybridization rate \citep{parker1998}  may create an often overlooked hurdle to the evolution of reinforcement.   
We develop a population genetic model of interspecific sexual conflict and show that it prevents the long term maintenance of reinforcement.  
We suggest that interspecific sexual conflict may be particularly severe after mating, hampering the reinforcement of postmating-prezygotic reproductive isolating barriers.

SENTENCE ABOUT REINFORCEMENT IN SYMPATRY
The process of reinforcement has gained widespread acceptance due to theoretical models showing its plausibility (CITE), lab experiments showing its evolution (CITE), and correlative studies showing its signature (CITE).  
The most compelling cases of reinforcement involve premating barriers. 
In addition to Coyne and Orr's \citeyearpar{coyneandorrbook} and other \citeyearpar{coyneandorr1989, coyneandorr1997} demonstrations of enhanced behavioral isolation of sympatric Drosophila species, the reinforcement of premating barriers has been documented in numerous taxa, including damselflies \citep{waage1979},  frogs \citep{blair1974, littlejohn1968, hobel2003}, fish \citep{rundle1998}, birds \citep{ratcliffe1983,saetre1997}, and plants \citep{hopkins2013}. %YOU WROTE: "Newer refs? These look old/classic. I have not read them all.. wonder if they show reinforcement or reproductive character displacement" I AM GOING TO LEAVE THIS FOR YOU YANIV

% MOVE TO END OF FIRST PARAGRAPH? MORE PREMATING VS POSTMATING SETUP 
While standard theory does not differentiate between the reinforcement of premating  and postmating-prezygotic [i.e. gametic] barriers, ``bona fide cases of reinforcement and of gametic isolation are still rare'' \citep{turissini2018}. %YANIV CAN YOU CHECK THIS QUOTE?
In fact, we know of only two unequivocal cases. 
First, the wild gingers species,  \textit{Costus scaber}, preferentially rejects  \textit{C. pulverulentus} pollen when the populations are sympatric, but not when they are allopatric \citep{kay2008}.  %pollen-pistil incompatibility, postmating prezygotic
Second, the extent of gametic isolation between \textit{Drosophila yakuba} females and \textit{D. santomea} males is stronger for sympatric than allopatric \textit{D. yakuba} samples \citep{matute2010}. 
Counter to these two examples, comparative surveys in both \textit{Drosophila} \citep{turissini2018} and plants \citep{moyle2004} fail to find a broad signature of reinforcement of postmating-prezygotic barriers. 
There are few other plausible cases of postmating-prezygotic reinforcement in maize \citep{kermicle2006}, sea urchins \citep{lessios2007,geyer2003,zigler2003}, and mussels \citep{slaughter2008}, however, these appear to involve barriers that are ineffective \citep{slaughter2008} and/or reflect the action of selection on intraspecific matings \citep{geyer2009}.

Interspecific sexual conflict could explain the difference in the frequency of reinforcement of premating and postmating-prezygotic barriers.   
Sexual conflict arises when different reproductive strategies maximize the fitness of each sex.    
 Sexual conflict in interspecific reproductive interactions can occur when the sexes `disagree' on the optimal hybridization rates \citep{parker1998}.  
The extent of this disagreement will reflect sex-specific differences in the trade-off between intraspecific and interspecific reproductive success, but is likely to be more intense for postmating barriers.
Consider the fate of a sperm (or pollen grain) in the reproductive tract of a heterospecific female. 
Without sperm limitation and with nonzero hybrid fitness, male fitness will increase and female fitness will decrease when sperm fertilize heterospecific eggs.   
In this case, selection will favor mechanisms by which male gametes overcome postmating barriers in females of other species, preventing reinforcement and breaking down reproductive isolation between species.   
By contrast, the reinforcement of pre-mating barriers may involve less conflict, because a trait preferred by conspecifics is disfavored by heterospecifics.   
Of course this distinction is not absolute --  the extent of sexual conflict will depend on how mechanistic details of premating and postmating interactions mediate the  sex-specific tradeoff between inter- and intraspecific reproductive success.

>>>>

Matings between sufficiently diverged populations or species produce low fitness hybrids, or fail altogether, due to the action of intrinsic incompatibilities \citep{dobzhansky1937, muller1942} or ecological barriers \citep{schluter1998}. 
% ALI: YANIV DOUBLE CHECK THIS REFERENCE IS ABOUT ECOLOGICAL BARRIERS 
% Yaniv: DONE~!
Misallocated reproductive effort spent on producing low fitness hybrids can be prevented through natural selection favoring prezygotic barriers, a process known as reinforcement \citep{dobzhansky1937, servedio2003}.
Reinforcement is generally conceptualized as the evolution of an assortative mating locus \citep{felsenstein1981} or female preference locus \citep{servedio1997}.   
Both reinforcement mechanisms assume males and females have a shared interest in preventing the production of low-fitness hybrid offspring. 
However, reproductive interactions are generally more fractious than this, as the costs of reproductive effort can differ by sex and reproductive stage (ranging from gamete formation to mating itself) \citep{arnqvistandrowebook}.  
Because male and female interests are not always aligned, interspecific sexual conflict over the hybridization rate \citep{parker1998}  may create an often overlooked hurdle to the evolution of reinforcement.   
We develop a population genetic model of interspecific sexual conflict and show that it prevents the long term maintenance of reinforcement.  
We suggest that interspecific sexual conflict may be particularly severe after mating, hampering the reinforcement of postmating-prezygotic reproductive isolating barriers.

The process of reinforcement has gained widespread acceptance due to theoretical models showing its plausibility \citep{Liou1994, servedio1997}, lab experiments showing its evolution \citep{koopman1950, matute2010}, and correlative studies showing its signature.   
These correlative studies compare the extent of prezygotic isolation (or some proxy for it, such as male trait divergence) between allopatric and sympatric populations of the same species pair, under the assumption that reinforcement can result in the elevation of reproductive isolation in sympatry, but will not occur in allopatry where there is no force to favor its evolution. 
% Yaniv tried explaining the allopatry sympatry thing
Most notably Coyne and Orr  \citeyearpar{coyneandorr1989, coyneandorr1997} documented enhanced behavioral isolation of sympatric Drosophila species, and similar observations have been found in numerous animals \citep[revivewed in ][]{coyneandorrbook} and plants \citep{hopkins2013}.  
% the reinforcement of premating barriers has been documented in numerous taxa, including damselflies \citep{waage1979},  frogs \citep{blair1974, littlejohn1968, hobel2003}, fish \citep{rundle1998}, birds \citep{ratcliffe1983,saetre1997}, and plants \citep{hopkins2013}. 
%ALI: YOU WROTE: "Newer refs? These look old/classic. I have not read them all.. wonder if they show reinforcement or reproductive character displacement" I AM GOING TO LEAVE THIS FOR YOU YANIV
% Yaniv: IHope this is ok?

% MOVE TO END OF FIRST PARAGRAPH? MORE PREMATING VS POSTMATING SETUP ... 
While standard theory does not differentiate between the reinforcement of premating  and postmating-prezygotic [i.e. gametic] barriers, ``bona fide cases of reinforcement and of gametic isolation are still rare'' \citep{turissini2018}. %YANIV CAN YOU CHECK THIS QUOTE? % YB: checked! 
In fact, we know of only two unequivocal cases. 
First, the wild gingers species,  \textit{Costus scaber}, preferentially rejects  \textit{C. pulverulentus} pollen when the populations are sympatric, but not when they are allopatric \citep{kay2008}.  %pollen-pistil incompatibility, postmating prezygotic
Second, the extent of gametic isolation between \textit{Drosophila yakuba} females and \textit{D. santomea} males is stronger for sympatric than allopatric \textit{D. yakuba} samples \citep{matute2010}. 
Counter to these two examples, comparative surveys in both \textit{Drosophila} \citep{turissini2018} and plants \citep{moyle2004} fail to find a broad signature of reinforcement of postmating-prezygotic barriers. 
There are few other plausible cases of postmating-prezygotic reinforcement in maize \citep{kermicle2006}, sea urchins \citep{lessios2007,geyer2003,zigler2003}, and mussels \citep{slaughter2008}, however, these appear to involve barriers that are ineffective \citep{slaughter2008} and/or reflect the action of selection on intraspecific matings \citep{geyer2009}.

Interspecific sexual conflict could explain the difference in the frequency of reinforcement of premating and postmating-prezygotic barriers.   
Sexual conflict arises when different reproductive strategies maximize the fitness of each sex.    
Sexual conflict in interspecific reproductive interactions can occur when the sexes `disagree' on the optimal hybridization rates \citep{parker1998}.  
The extent of this disagreement will reflect sex-specific differences in the trade-off between intraspecific and interspecific reproductive success, but is likely to be more intense for postmating barriers, because postmating isolation follows the expenditure of male reproductive effort.
Consider the fate of a sperm (or pollen grain) in the reproductive tract of a heterospecific female. 
Without sperm limitation and with nonzero hybrid fitness, male fitness will increase and female fitness will decrease when sperm fertilize heterospecific eggs.   
In this case, selection will favor mechanisms by which male gametes overcome postmating barriers in females of other species, preventing reinforcement and breaking down reproductive isolation between species.   
By contrast, the reinforcement of pre-mating barriers may involve less conflict, because a trait preferred by conspecifics is disfavored by heterospecifics.   
Of course this distinction is not absolute --  the extent of sexual conflict will depend on how mechanistic details of premating and postmating interactions mediate the  sex-specific tradeoff between inter- and intraspecific reproductive success - for example, conspecific gamete precedence or other forms of postmating prezygotic isolation could evolve if reproductive success with heterospecifics comes at a cost of conspecific fertilization success .
